Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-06 ijar-npb-ms.tex
Figs 5,6,7,8 updated (ggplot2 changes), text adjusted to T1 <-> T3 change

As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
as depicted in Figure~\ref{fig:bridge-layout}.
For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
For components of type T3, we consider an informative set of prior reliability functions
as given in Table~\ref{tab:bridge-T3prior}.
This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
and filling up the rest.
These prior assumptions, together with sets of posterior reliability functions
resulting from three different scenarios for test data for component type T3,
are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
test data for components of type T1 and T2 are invariably taken as
$\vec{t}^1 = (2.0, 2.2, 2.4, 2.6)$ and $\vec{t}^2 = (3.0, 3.2, 3.4, 3.6)$, respectively.

@@

In Figure~\ref{fig:bridge-fitting}, 
test data for component type T3 is $\vec{t}^3 = (0.5, 1.5, 2.5, 3.5)$,
and so in line with expectations.
The posterior set of reliability functions for each component type and the whole system
is considerably smaller as compared to the prior set
(due to the low prior strength intervals
$[\ntzl{1},\ntzu{1}] = [\ntzl{2},\ntzu{2}] = [1,2]$, $[\ntzl{3},\ntzu{3}] = [1,4]$)
and so giving more precise reliability statements.
We see that posterior lower and upper functioning probabilities drop at those times $t$
when there is a failure time in the test data,
or a drop in the prior functioning probability bounds.
Note that the lower bound for prior system reliability function is zero
due to the prior lower bound of zero for T1;
for the system to function, the component of type T1 must function.

@@

In Figure~\ref{fig:bridge-late}, 
test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
and so observed failures are later than expected.
Here we see that for $t \in [2,4]$,
posterior functioning bounds for T3 are even wider than prior functioning bounds.
The width turns back to being half the prior width
only after the four failures.
The imprecision carries over to the system bounds,
where we see wider bounds as compared to the other scenarios
especially between $t=2$ and $t=4$.

@@

\begin{figure}
\begin{tikzpicture}
[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-1}};
\begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]
\node[typeM] (M)    at ( 0  , 0  ) {M};
\node[typeC] (C1)   at ( 1  , 1.5) {C1};
\node[typeC] (C2)   at ( 1  , 0.5) {C2};
\node[typeC] (C3)   at ( 1  ,-0.5) {C3};
\node[typeC] (C4)   at ( 1  ,-1.5) {C4};
\node[typeP] (P1)   at ( 2  , 1.5) {P1};
\node[typeP] (P2)   at ( 2  , 0.5) {P2};
\node[typeP] (P3)   at ( 2  ,-0.5) {P3};
\node[typeP] (P4)   at ( 2  ,-1.5) {P4};
\node[typeH] (H)    at ( 0  ,-1  ) {H};
\coordinate (start)  at (-0.7, 0);
\coordinate (startC) at ( 0.5, 0);
\coordinate (startH) at (-0.4, 0);
\coordinate (Hhop1)  at ( 0.4,-1);
\coordinate (Hhop2)  at ( 0.6,-1);
\coordinate (endP)   at ( 2.5, 0);
\coordinate (end)    at ( 2.8, 0);
\path (start)     edge[hv path] (M.west)
      (M.east)    edge[hv path] (startC)
      (startC)    edge[vh path] (C1.west)
                  edge[vh path] (C2.west)
                  edge[vh path] (C3.west)
                  edge[vh path] (C4.west)
      (C1.east)   edge[hv path] (P1.west)
      (C2.east)   edge[hv path] (P2.west)
      (C3.east)   edge[hv path] (P3.west)
      (C4.east)   edge[hv path] (P4.west)
      (endP)      edge[vh path] (P1.east)
                  edge[vh path] (P2.east)
                  edge[vh path] (P3.east)
                  edge[vh path] (P4.east)
                  edge[hv path] (end)
      (startH)    edge[vh path] (H.west)
      (H.east)    edge[hv path] (Hhop1)
      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
      (Hhop2)     edge[hv path] (P3.south)
                  edge[hv path] (P4.north);
\end{scope}
\end{tikzpicture}
\caption{Prior and posterior sets of reliability functions for a simplified automotive breaking system
with layout as depicted in the lower right panel.}
\label{fig:breakingsystem}
\end{figure}

>>>>

As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
as depicted in Figure~\ref{fig:bridge-layout}.
For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
For components of type T3, we consider an informative set of prior reliability functions
as given in Table~\ref{tab:bridge-T3prior}.
This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
and filling up the rest.
These prior assumptions, together with sets of posterior reliability functions
resulting from three different scenarios for test data for component type T3,
are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
test data for components of type T1 and T2 are invariably taken as
$\vec{t}^1 = (2.2, 2.4, 2.6, 2.8)$ and $\vec{t}^2 = (3.2, 3.4, 3.6, 3.8)$, respectively.

@@

In Figure~\ref{fig:bridge-fitting}, 
test data for component type T3 is $\vec{t}^3 = (0.5, 1.5, 2.5, 3.5)$,
and so in line with expectations.
The posterior set of reliability functions for each component type and the whole system
is considerably smaller as compared to the prior set
(due to the low prior strength intervals
$[\ntzl{1},\ntzu{1}] = [\ntzl{2},\ntzu{2}] = [1,2]$, $[\ntzl{3},\ntzu{3}] = [1,4]$)
and so giving more precise reliability statements.
We see that posterior lower and upper functioning probabilities drop at those times $t$
when there is a failure time in the test data,
or a drop in the prior functioning probability bounds.
Note that the lower bound for prior system reliability function is zero
due to the prior lower bound of zero for T1;
for the system to function, at least two components of type T1 must function.

@@

In Figure~\ref{fig:bridge-late}, 
test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
and so observed failures are later than expected.
Here we see that for $t \in [2,4]$,
posterior functioning bounds for T3 are even wider than prior functioning bounds.
The width turns back to being half the prior width
only after the four failures.
The imprecision carries over to the system bounds,
where we see wider bounds as compared to the other two scenarios
especially between $t=2$ and $t=4$.

@@

\begin{figure}
\begin{tikzpicture}
[typeM/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeC/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeP/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 typeH/.style={rectangle,draw,fill=black!20,thick,inner sep=0pt,minimum size=5mm,font=\footnotesize},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
\node at (0,0) {\includegraphics[width=\textwidth]{breakingsystem-2}};
\begin{scope}[scale=1.00,xshift=3.4cm,yshift=-1.1cm]
\node[typeM] (M)    at ( 0  , 0  ) {M};
\node[typeC] (C1)   at ( 1  , 1.5) {C1};
\node[typeC] (C2)   at ( 1  , 0.5) {C2};
\node[typeC] (C3)   at ( 1  ,-0.5) {C3};
\node[typeC] (C4)   at ( 1  ,-1.5) {C4};
\node[typeP] (P1)   at ( 2  , 1.5) {P1};
\node[typeP] (P2)   at ( 2  , 0.5) {P2};
\node[typeP] (P3)   at ( 2  ,-0.5) {P3};
\node[typeP] (P4)   at ( 2  ,-1.5) {P4};
\node[typeH] (H)    at ( 0  ,-1  ) {H};
\coordinate (start)  at (-0.7, 0);
\coordinate (startC) at ( 0.5, 0);
\coordinate (startH) at (-0.4, 0);
\coordinate (Hhop1)  at ( 0.4,-1);
\coordinate (Hhop2)  at ( 0.6,-1);
\coordinate (endP)   at ( 2.5, 0);
\coordinate (end)    at ( 2.8, 0);
\path (start)     edge[hv path] (M.west)
      (M.east)    edge[hv path] (startC)
      (startC)    edge[vh path] (C1.west)
                  edge[vh path] (C2.west)
                  edge[vh path] (C3.west)
                  edge[vh path] (C4.west)
      (C1.east)   edge[hv path] (P1.west)
      (C2.east)   edge[hv path] (P2.west)
      (C3.east)   edge[hv path] (P3.west)
      (C4.east)   edge[hv path] (P4.west)
      (endP)      edge[vh path] (P1.east)
                  edge[vh path] (P2.east)
                  edge[vh path] (P3.east)
                  edge[vh path] (P4.east)
                  edge[hv path] (end)
      (startH)    edge[vh path] (H.west)
      (H.east)    edge[hv path] (Hhop1)
      (Hhop1)     edge[thick,out=90,in=90] (Hhop2)
      (Hhop2)     edge[hv path] (P3.south)
                  edge[hv path] (P4.north);
\end{scope}
\end{tikzpicture}
\caption{Prior and posterior sets of reliability functions for a simplified automotive breaking system
with layout as depicted in the lower right panel.}
\label{fig:breakingsystem}
\end{figure}
